\documentclass[a4paper, 12pt]{scrartcl}
  % Headers and footers.
  \usepackage{fancyhdr}
  % Enables the use of colour.
  \usepackage{xcolor}
  % Syntax high-lighting for code. Requires Python's pygments.
  \usepackage{minted}
  % Enables the use of umlauts and other accents.
  \usepackage[utf8]{inputenc}
  % Diagrams.
  \usepackage{tikz}
  % Settings for captions, such as sideways captions.
  \usepackage{caption}
  % Symbols for units, like degrees and ohms.
  \usepackage{gensymb}
  % Latin modern fonts - better looking than the defaults.
  \usepackage{lmodern}
  % Allows for columns spanning multiple rows in tables.
  \usepackage{multirow}
  % Better looking tables, including nicer borders.
  \usepackage{booktabs}
  % More math symbols.
  \usepackage{amssymb}
  % More math fonts, like \mathbb.
  \usepackage{amsfonts}
  % More math layouts, equation arrays, etc.
  \usepackage{amsmath}
  % More theorem environments.
  \usepackage{amsthm}
  % More column formats for tables.
  \usepackage{array}
  % Adjust the sizes of box environments.
  \usepackage{adjustbox}
  % Better looking single quotes in verbatim and minted environments.
  \usepackage{upquote}
  % Better blank space decisions.
  \usepackage{xspace}
  % Better looking tikz trees.
  \usepackage{forest}
  % URLs.
  \usepackage[hidelinks]{hyperref}
  % Plotting.
  \usepackage{pgfplots}
  % Calculates the number of pages.
  \usepackage{lastpage}
  % Styling the abstract.
  \usepackage{abstract}

  
  % Various tikz libraries.
  % For drawing mind maps.
  \usetikzlibrary{mindmap}
  % For adding shadows.
  \usetikzlibrary{shadows}
  % Extra arrows tips.
  \usetikzlibrary{arrows.meta}
  % Old arrows.
  \usetikzlibrary{arrows}
  % Automata.
  \usetikzlibrary{automata}
  % For more positioning options.
  \usetikzlibrary{positioning}
  % Creating chains of nodes on a line.
  \usetikzlibrary{chains}
  % Fitting node to contain set of coordinates.
  \usetikzlibrary{fit}
  % Extra shapes for drawing.
  \usetikzlibrary{shapes}
  % For markings on paths.
  \usetikzlibrary{decorations.markings}
  % For advanced calculations.
  \usetikzlibrary{calc}
  
  % GMIT colours.
  \definecolor{gmitblue}{RGB}{20,134,225}
  \definecolor{gmitred}{RGB}{220,20,60}
  \definecolor{gmitgrey}{RGB}{67,67,67}

  % Set minted up.
  \usemintedstyle{manni}
  \setminted{baselinestretch=1.2, bgcolor=gmitgrey!10}

  % Change the displayed name of the references section.
  \renewcommand{\refname}{\selectfont\large References} 

  % Heading
  \title{Tasks 2020}
  \author{Emerging Technologies}
  \date{Due: last commit on or before December 18\textsuperscript{th}, 2020}

\begin{document}
  
  \maketitle

  This document contains the instructions for the tasks for Emerging Technologies in the first semester of the 2020/2021 academic year.
  This assessment is worth 50\% of the total marks for the module.
  Students should carefully read the document \emph{Using git for assessments}~\cite{usinggit} that is available on the Moodle page and applies to this assessment.
  Students are also reminded to follow the GMIT Quality Assurance Framework including the Code of Student Conduct and the policy on plagiarism~\cite{gmitqaf}.

  \section*{Instructions}
  You should complete the following four tasks in one jupyter notebook in a single git repository.
  This repository should be submitted using the correct link on the Moodle page.
  The tasks should each ideally be completed within two week of them being made available.
  It is important that you continuously work on the repository throughout the semester.
  \begin{enumerate}
    \item
      \textbf{October 5\textsuperscript{th}, 2020:} Write a Python function called \mintinline{python}{sqrt2} that prints to the screen the square root of 2 to 100 decimal places.
      Your code should not depend on any other module, in the standard library or otherwise.
      You should research the task before attempting it, and include references and a description of your algorithm in a Markdown box above the code.
  \end{enumerate}


\newpage

\section*{Marking scheme}
  The following marking scheme will be used to mark your submission out of 100\%, which will then be scaled to 50\%.
  The examiner's overall impression of the assignment may influence marks in each individual component.
  Also, it is important that your submission provides direct evidence of each of the items listed in each category.
  For instance, your commit history should demonstrate and provide evidence that you had a pragmatic attitude to completing the assessment.
  Likewise, your submission should have references in it to demonstrate that you considered the literature and the work of others.

  \begin{center}
    \begin{tabular}{llp{8.4cm}}
      \toprule
      25\% & \textbf{Research} & Evidence of research performed on topic; submission based on referenced literature, particularly academic literature; evidence of understanding of the documentation for any software or libraries used. \\
      \midrule
      25\% & \textbf{Development} & Environment can be set up as described; code works without tweaking and as described; code is efficient, clean, and clear; evidence of consideration of standards and conventions appropriate to code of this kind. \\
      \midrule
      25\% & \textbf{Consistency} & Evidence of planning and project management; pragmatic attitude to work as evidenced by well-considered commit history; commits are of a reasonable size; evidence of consideration. \\
      \midrule
      25\% & \textbf{Documentation} & Clear documentation of: how to create an environment in which any code will run, how to prepare the code for running, how to run the code including setting any options or flags, what to expect upon running the code. Concise descriptions of any code in comments and README. \\
      \bottomrule
    \end{tabular}
  \end{center}
  



  \bibliographystyle{plain}
  \bibliography{bibliography}

\end{document}
